All Samples Model

### 2018-03-27 AllSamplesModel.Rmd
updating shiny app

```{r prediction_cutoff, echo=F, message=F, warning=F, fig.height=7, fig.width=7}
preds = do.call(rbind.data.frame, lapply(pg.samp, function(df) df[c('Status','Prediction')]))
roc = pROC::roc(Status ~ Prediction, data=preds, auc=T, ci=T, of='thresholds')
roc$model = 'CN Model'
roc$is = 'all'

@@

@@

```{r pathroc, echo=F, fig.height=4, fig.width=10 }
pathsamples = patient.info[,c('Pathology','Status')]
pathroc = pROC::roc((as.integer(pathsamples$Status)-1), ifelse(pathsamples$Pathology %in% c('LGD','HGD','IMC'), 1, 0) )
pathroc$model = 'HGD & LGD'
ggsave('plots/auc/dysplasia_auc.png', plot=roc.plot(pathroc, title='Dysplasia (HGD & LGD)'), width=6, height=6, units="in", limitsize=F, dpi = 300)

hgdpathroc = pROC::roc((as.integer(pathsamples$Status)-1), ifelse(pathsamples$Pathology %in% c('HGD','IMC'), 1, 0) )
hgdpathroc$model = 'HGD Only'
ggsave('plots/auc/hgd_auc.png', plot=roc.plot(hgdpathroc, title='HGD Only'), width=6, height=6, units="in", limitsize=F, dpi = 300)

@@

  stat = rbind('AUC'=auc, 'Sensitivity'=sens[c(1,2,4)], 'Specificity'=spec[c(1,2,4)])
  colnames(stat) = c ('value','CI.min','CI.max')
  stat = as.data.frame(stat)
  stat$model = roc$model
  stat$Measure = rownames(stat)
  stat
}

get.auc.at<-function(roc, foc='spec', p=c(1,0.99)) {
  # To find the auc at a given spec or sens
  pROC::auc(roc, partial.auc=p, partial.auc.focus=foc, partial.auc.correct=T)
}

roc$model = "CN Model"
m = rbind.data.frame(
  get.roc.stat(p53roc),
  get.roc.stat(hgdpathroc),
  get.roc.stat(pathroc),
  get.roc.stat(roc))
m$model = factor(m$model, levels=c('p53 IHC', 'HGD Only','HGD & LGD','CN Model'), ordered = T)

@@

@@

>>>>

```{r prediction_cutoff, echo=F, message=F, warning=F, fig.height=7, fig.width=7}
preds = do.call(rbind.data.frame, lapply(pg.samp, function(df) df[c('Status','Prediction')]))
roc = pROC::roc(Status ~ Prediction, data=preds, auc=T, ci=T, of='thresholds')
roc$model = 'CN Model'

pROC::ci.auc(roc)

roc$is = 'all'

@@

pROC::ci.auc(p53roc)

@@

```{r pathroc, echo=F, fig.height=4, fig.width=10 }
pathsamples = patient.info[,c('Pathology','Status')]
pathroc = pROC::roc((as.integer(pathsamples$Status)-1), ifelse(pathsamples$Pathology %in% c('LGD','HGD','IMC'), 1, 0) )
pathroc$model = 'HGD & LGD'

pROC::ci.auc(pathroc)

ggsave('plots/auc/dysplasia_auc.png', plot=roc.plot(pathroc, title='Dysplasia (HGD & LGD)'), width=6, height=6, units="in", limitsize=F, dpi = 300)

hgdpathroc = pROC::roc((as.integer(pathsamples$Status)-1), ifelse(pathsamples$Pathology %in% c('HGD','IMC'), 1, 0) )
hgdpathroc$model = 'HGD Only'

pROC::ci.auc(hgdpathroc)

ggsave('plots/auc/hgd_auc.png', plot=roc.plot(hgdpathroc, title='HGD Only'), width=6, height=6, units="in", limitsize=F, dpi = 300)

@@

  stat = rbind('AUC'=auc, 'Sensitivity'=sens[c(1,2,4)], 'Specificity'=spec[c(1,2,4)])
  colnames(stat) = c ('value','CI.min','CI.max')
  stat = as.data.frame(stat)
  stat$model = roc$model
  stat$Measure = rownames(stat)
  stat
}
roc$model = "CN Model"
m = rbind.data.frame(
  get.roc.stat(p53roc),
  get.roc.stat(hgdpathroc),
  get.roc.stat(pathroc),
  get.roc.stat(roc))
m$model = factor(m$model, levels=c('p53 IHC', 'HGD Only','HGD & LGD','CN Model'), ordered = T)

@@

subset(m, model %in% c(rocEndoA$model, rocEndoM$model) & Measure == 'AUC')

@@

fisher.test(table(pi$p11Loss, pi$p53.Status))
